Differential expression figures

### 2018-01-26 manuscriptFigures/diffExpFigure.Rmd
Minor changes

---
title: "Differential expression figures"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_notebook
---
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
# Load required libraries
library(CovariateAnalysis)
library(data.table)
library(plyr)
library(tidyverse)

library(synapseClient)
library(githubr)
library(knitr)

@@

    if (unique(x$Direction) == 'Up'){
      col = c('white','red')
    } else {
      col = c('white','darkgreen')
    }
    ComplexHeatmap::Heatmap(as.matrix(or.mat), 
                            col= circlize::colorRamp2(c(0,40),col),
                            cell_fun = function(j, i, x, y, widht, height, fill){
                              no.mat[i,j] %>%
                                format(digit = 1) %>%
                                as.character() %>%
                                grid.text(x, y)
                            },
                            name = 'Odds Ratio',
                            column_title = paste(unique(x$Direction), 
                                                 'regulated in', 
                                                 unique(x$Gender)))
  })
purrr::walk(dexp.enrich.plots, function(x){ print(x) })
```
### Store in synapse
```{r syn.store}
# Get github commit
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Network", ref="branch", refName='AMPAD_manuscript')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('manuscriptFigures/',thisFileName))

obj = rmarkdown::render('diffExpFigure.Rmd', output_format = 'html_document')
obj = File(obj, name = 'Differential expression summary', parentId = 'syn11703045')
obj = synStore(obj, executed = thisFile)
# wikiPg = WikiPage(owner = obj, title = 'Figure1')
wikiPg = synGetWiki(obj)
wikiPg@properties$markdown = paste0("${preview?entityId=",obj$properties$id,"}")
wikiPg = synStore(wikiPg)
```

>>>>

---
title: "Differential expression figures"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_notebook
---
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
# Load required libraries
library(CovariateAnalysis)
library(data.table)
library(plyr)
library(tidyverse)
library(ComplexHeatmap)
library(circlize)
library(gridExtra)
library(synapseClient)
library(githubr)
library(knitr)

@@

    if (unique(x$Direction) == 'Up'){
      col = c('white','red')
    } else {
      col = c('white','darkgreen')
    }
    ComplexHeatmap::Heatmap(as.matrix(or.mat), 
                            col= circlize::colorRamp2(c(0,40),col),
                            cell_fun = function(j, i, x, y, widht, height, fill){
                              no.mat[i,j] %>%
                                format(digit = 1) %>%
                                as.character() %>%
                                grid.text(x, y)
                            },
                            name = 'Odds Ratio',
                            column_title = paste(unique(x$Direction), 
                                                 'regulated in', 
                                                 unique(x$Gender)))
  })
purrr::walk(dexp.enrich.plots, function(x){ print(x) })
```
### Store in synapse
```{r syn.store, eval = FALSE, include = FALSE}
# Get github commit
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD_manuscript')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('manuscriptFigures/diffExpFigure.Rmd'))

obj = rmarkdown::render('diffExpFigure.Rmd', output_format = 'html_document')
obj = File(obj, name = 'Differential expression summary', parentId = 'syn11703045')
obj = synStore(obj, executed = thisFile)
wikiPg = WikiPage(owner = obj, title = 'Differential expression summary')
wikiPg = synGetWiki(obj)
wikiPg@properties$markdown = paste0("${preview?entityId=",obj$properties$id,"}")
wikiPg = synStore(wikiPg)
```
